A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-09 paper/paper.tex
Added another future work item
Changed some figures of algorithm walkthrough to tables

% TODO: use operatorname for these
\DeclareMathOperator{\V}{V}
\DeclareMathOperator{\E}{E}

@@

Given graphs $G=(\V(G), \E(G))$ and $H=(\V(H), \E(H))$, the \emph{Maximum Common
Subgraph (MCS)} problem is to find a graph with as many vertices as possible
that is isomorphic to induced subgraphs of both $G$ and $H$.

@@

\begin{figure}[ht]
\centering
    \examplexG{}{}{}{}{}
    \examplexH{}{}{}{}{}{}
\caption{Graphs $G$ and $H$}
\label{fig:alg1}
\end{figure}

@@

\begin{figure}[ht]
\centering
    \examplexG{$(1a)$}{0}{0}{1}{1}
    \examplexH{$(1a)$}{1}{1}{0}{1}{0}
\caption{Step 2}
\label{fig:alg2}
\end{figure}

@@

\begin{figure}[ht]
\centering
    \examplexG{$(1a)$}{$(2d)$}{01}{10}{11}
    \examplexH{$(1a)$}{11}{11}{$(2d)$}{10}{01}
\caption{Step 3}
\label{fig:alg3}
\end{figure}

@@

>>>>

% TODO: use operatorname for these
\DeclareMathOperator{\V}{V}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\N}{N}

@@

Given graphs $G$ and $H$, the \emph{Maximum Common Subgraph (MCS)} problem is
to find a graph with as many vertices as possible that is isomorphic to induced
subgraphs of both $G$ and $H$.

@@

\begin{figure}[ht]
\centering
    \includegraphics{graph_G}
    \includegraphics{graph_H}
%    \examplexG{}{}{}{}{}
%    \examplexH{}{}{}{}{}{}
\caption{Graphs $G$ and $H$}
\label{fig:alg1}
\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{minipage}[t]{0.15\linewidth}
    Mapping

    \bigskip

    $\{1a\}$
\end{minipage}
\quad
\begin{minipage}[t]{0.3\linewidth}
    Labelling of $G$
    \begin{tabular}[t]{cc}
    \hline
        Vertex & Label\\
    \hline
        $2$ & 0 \\
        $3$ & 0 \\
        $4$ & 1 \\
        $5$ & 1 \\
    \hline
    \end{tabular}
\end{minipage}
\quad
\begin{minipage}[t]{0.3\linewidth}
    Labelling of $H$
    \begin{tabular}[t]{cc}
    \hline
        Vertex & Label\\
    \hline
        $b$ & 1 \\
        $c$ & 1 \\
        $d$ & 0 \\
        $e$ & 1 \\
        $f$ & 0 \\
    \hline
    \end{tabular}
\end{minipage}
    \caption{Labels on vertices after mapping $1$ to $a$}
\label{fig:alg2}
\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{minipage}[t]{0.15\linewidth}
    Mapping

    \bigskip

    $\{1a, 2d\}$
\end{minipage}
\quad
\begin{minipage}[t]{0.3\linewidth}
    Labelling of $G$
    \begin{tabular}[t]{cc}
    \hline
        Vertex & Label\\
    \hline
        $3$ & 01 \\
        $4$ & 10 \\
        $5$ & 11 \\
    \hline
    \end{tabular}
\end{minipage}
\quad
\begin{minipage}[t]{0.3\linewidth}
    Labelling of $H$
    \begin{tabular}[t]{cc}
    \hline
        Vertex & Label\\
    \hline
        $b$ & 11 \\
        $c$ & 11 \\
        $e$ & 10 \\
        $f$ & 01 \\
    \hline
    \end{tabular}
\end{minipage}
\caption{Step 3}
\label{fig:alg3}
\end{figure}

@@

Parallel versions: bitset and multithreaded
